Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-10-02 paper.tex
Clarify computational domain size for rev 2

The computational domain was a rectangular volume 3.66 m long, 3.66 m wide, and
2.44 m tall (for 3-D), with the turbine located 1.52 m from the inlet, and
centered vertically with a vertical axis, designed to match the tow tank
dimensions for comparison with previous experiments. The rotor geometry was
located at the center of a cylindrical sliding mesh interface, which rotated at
a mean tip speed ratio $\lambda=1.9$ with a sinusoidal oscillation at the blade
passage frequency---with and amplitude of 0.19 and the first peak at 1.4
radians---to mimic the slight deviation from the mean tip speed ratio observed
in the experiments. The 2-D mesh overview is shown in
Figure~\ref{fig:2d-br-mesh} and the blade mesh detail is shown in
Figure~\ref{fig:blade-mesh}.

>>>>

The computational domain was designed to match the tow tank dimensions for
comparison with previous experiments. Thus, it was modeled as a rectangular
volume 3.66 m long, 3.66 m wide, and 2.44 m tall (for the 3-D cases), with the
turbine located 1.52 m from the inlet, centered within the tank depth with its
axis oriented vertically. The rotor geometry was located at the center of a
cylindrical sliding mesh interface, which rotated at a mean tip speed ratio
$\lambda=1.9$ with a sinusoidal oscillation at the blade passage
frequency---with and amplitude of 0.19 and the first peak at 1.4 radians---to
mimic the slight deviation from the mean tip speed ratio observed in the
experiments. The 2-D mesh overview is shown in Figure~\ref{fig:2d-br-mesh} and
the blade mesh detail is shown in Figure~\ref{fig:blade-mesh}.
